Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-23 paper/egpaper_for_review.tex
add grid parameter search plots

\section{Experiments}
\subsection{Benchmark Models}

>>>>

\section{Experiments}

\subsection{Parameter Choice}
\begin{figure}
\centering
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time.pdf}}
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value.pdf}}
\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
}
\end{figure}

\subsection{Benchmark Models}
